---
title: "Simple Analysis"
output: html_notebook
---

First, we import the raw data. Columns represent the tRNA modifications and rows represent mutant type. We reserve the first column for wild type. 

```{r}
library("readxl");
df = data.frame(read.csv("rawdata.csv"));
```

Verify that the import was successful. Dimensions of data should now be nonzero. 

```{r}
print(dim(df))
print(dimnames(df))
```
Remove last four (rC, rU, rG, rA) from our data value and put it into standard_data variable. 

```{r}
standard_data = tail(df, 4)
df = head(df, -4)


```
Find Sum of the four values for rC, rU, rG, and rA

```{r}

standard_data = rbind(standard_data, data.frame(X = "Sum", t(colSums(standard_data[, -1]))));

sum_standard = t(as.numeric(tail(standard_data, n=1)[-1]))

typeof(sum_standard)

df[, unlist(lapply(df, is.numeric))]

lf = as.data.frame(df[, unlist(lapply(df, is.numeric))] / sum_standard)

lf



```
Standardize data via the sums
```{r}
data_matrix = data.matrix(df)
heatmap(data_matrix)
```

